### 2011-07-14 doc/theses/vitasek/diplomka.tex
Thesis: in progress.
Thesis: in progress

TODO why is this important - XMLs are extensively used but lack schemas (link Vosta's Even ant can create...).
We already have tools to infer the structure (see jInfer), now we would like to go a bit further - to find some integrity constraints to impose on these schemas.
Integrity schemas can be keys (with ID attributes as a "sub-group"), FKs, functional dependencies (quote Sviro?), etc.
We will focus on the first kind - ID and IDREF attributes.

@@

\begin{itemize}
	\item XML tree - from FIDAX or wherever
	\item Element, Attribute
	\item ID, IDREF, IDREFS attribute according to specification
	\item XSD keys (compare them to ID attributes)
	\item Key according to Keys for XML \cite{keX}
	\item Attribute mapping
	\item ID set
\end{itemize}

@@

TODO define IS rigorously

@@

TODO how GLPK works, how to construct a problem, how output looks, how to interpret it, limit time-> limit quality, ...

@@

@@

TODO types of data:
\begin{itemize}
	\item Realistic 
	\item Artificial
\end{itemize}

@@

@@

TODO these are random graphs.
TODO talk about how they are created, about their structure.
TODO talk about some "density".
TODO show a picture, possibly from GraphViz.

@@

TODO we will be using jInfer, see \ref{jInfer}.

@@

\begin{itemize}
  \item Which construction heuristic is the best - limit GLPK to like 1 second
  \item With the best construction heuristic, which IH is the best? Note that this needn't be the best combination!
  \item With the best IH from the previous step, how about using Random as CH?
	\item GLPK: Input -> How long the search for optimum lasts
	\item GLPK: Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
	\item Which GLPK -> *
	\item Do I beat FIDAX with Random?
	\item Does Fuzzy beat Random? (Seems that Random is better and even has smaller variance)
\end{itemize}

@@

@@

TODO conclusion

@@

\printnomenclature
\addcontentsline{toc}{chapter}{List of Abbreviations}

@@

>>>>

TODO why is this important - XMLs are extensively used but lack schemas (link Vosta's Even ant can create...).
We already have tools to infer the structure (see jInfer), now we would like to go a bit further - to find some integrity constraints to impose on these schemas.
Integrity schemas can be keys (with ID attributes as a "sub-group"), FKs, functional dependencies (quote Sviro), etc.
We will focus on the first kind - ID and IDREF attributes.

@@

\begin{itemize}
	\item XML tree - from FIDAX or wherever
	\item Element, Attribute
	\item ID, IDREF, IDREFS attribute according to specification
	\item XSD keys (compare them to ID attributes)
	\item Key according to Keys for XML \cite{keX}
	\item Attribute mapping
	\item ID set
  \item Weight: support, coverage
\end{itemize}

@@

TODO define IS + MIS rigorously

@@

TODO how GLPK works (branch&bound), how to construct a problem, how output looks, how to interpret it, limit time-> limit quality, ...

@@

TODO describe all the inputs (take it from the mindmap), describe how the output looks (sample trace - link to appendix)

@@

TODO types of data:
\begin{itemize}
	\item Realistic 
  \item Realistic with artificial attributes
	\item Artificial
\end{itemize}

TODO for all types, show GraphViz pictures.

@@

\subsection{Realistic data with artificial attributes}

TODO we have taken some of the text data and converted it to attributes like this, A B C

@@

TODO these are random graphs.
TODO talk about how they are created, about their structure.
TODO talk about some "density".

@@

TODO we will be using jInfer and its module AttributeStats see \ref{jInfer} and \ref{attrstats}.

@@

\begin{itemize}
  \item Which construction heuristic is the best - limit GLPK to like 1 second
  \item With the best construction heuristic, which IH is the best? Note that this needn't be the best combination!
  \item With the best IH from the previous step, how about using Random as CH?
	\item GLPK: Input -> How long the search for optimum lasts
	\item GLPK: Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
  \item Alpha, Beta -> How does the solution work?
	\item Which GLPK -> How does (time->quality) look, how does (input->time) look
	\item Do I beat FIDAX with Random?
	\item Does Fuzzy beat Random? (Seems that Random is better and even has smaller variance)
\end{itemize}

@@

\chapter{Future work}

TODO extension to more documents, IDREFs, ...

@@

TODO conclusion: From all integrity constraints in XML we chose the ID attributes and decided to improve the search for them. We discussed the approach chosen in FIDAX. Based on this article we introduced the MIP approach and demonstrated how to find the optimal (w.r.t. weight) ID set.

However, this approach takes too long for some inputs, so we introduced a whole spectrum of construction as well as improvement heuristics. By combining these algorithms and tuning their parameters we were able to find very good solutions while maintaining low running times.

@@

\printnomenclature[2cm]
\addcontentsline{toc}{chapter}{List of Abbreviations}

@@

TODO what it is, who created it and why, what it can do, where to get it.

\chapter{AttributeStats}
\label{attrstats}

TODO talk a bit about the structure of AttributeStats module.

\chapter{Traces}
\label{traces}

TODO a few (commented!) traces from experiment runs
